\documentclass[12pt]{article}
\usepackage[shortlabels]{enumitem}
\usepackage{placeins}
\usepackage{graphicx}
\begin{document}
\title{TCES 420 - Week 10}
\author{Jake McKenzie}
\maketitle
\noindent\centerline{\textbf{Homework 8}}
\textbf{1)}\\\\
1-Assume three periodic tasks in a real time system:\\\\
TA: $T=4$, $P=1$;
TB: $T=6$, $P=2$;
TC: $T=8$, $P=2$;\\\\
a)Apply Earliest Deadline Scheduling(EDS). Show your result in a timing diagram.\\\\
b)Is Rate Monotonic Scheduling (RMS) possible? 
Prove your point by a timing diagram sketch.\\\\
c)Replace TCwith (T=6, P=1). Repeat part b.\\\\
\textbf{2)}\\\\
Propose a method to implement EDS in RTX.\\\\
EDS, to my understanding, priority is is given out to each process 
dynamically based on each individual processes deadline. We can find what 
is known as a hyper period by taking the LCM of all the periods. This gives 
use the period for all the processes. The global interval can be found by 
taking the GCD of all the process intervals. The size of our table will then 
be the division of Global Period$/$Global Interval. The 
Table pointer is then $(i+1)\%$the size of the table.\\\\
If there is a change within processes to fix the issue, like with your Mars example,
you must decrement the prior task to last in the priority queue. This ensures there 
are no processes hogging up the queue.\\\\
\textbf{3)}\\\\
Propose a method to implement RMSin RTX.\\\\
RMS maps one-to-one to a real time operating system and lends itself well 
to RTOS for this reason.\\\\
\textbf{4)}\\\\
Propose a method to implement Earliest Start Timein RTX.\\\\
Sort the start deadlines by start deadlines then put them in a queue. This 
list of processes are now scheduled based on this queue. In the interrupt service 
routine a scheduler is implemented based on current state, where if the next state is 
different it switches priority. If there are no tasks to schedule, schedules the idle task.\\\\
\textbf{5)}\\\\
In a multicore system, on which processor(core?) the OS is running?\\\\
The OS can exist on any core at any time.
\end{document}